---
title       : XY - Plotter from csv files
subtitle    : 
author      : SAI TEJA
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---



## WHY CSV Data Visualizer?

*  App plots simple XY plot from an user defined csv file
*  Post Processing Data is essential for many applications especially in engineering
* Most common type of plots required are XY plots between two variables 
* Preliminary stage app which helps in plooting simple plots through R with out actually knowing R

---

## Sample CSV File

```{r}
data_csv = read.csv("C:/Users/saiteja/Documents/Coursera/developing data products/courseproj_slidify/CSVPlotter/data_sample.csv")
 data<-na.omit(data_csv)

head(data, n=5)
```

---
## Sample XY Plot

```{r}
library(ggplot2, quietly = TRUE)
qplot(data$DAY, data$Temperature, geom = "line")
```

---
## Uses

* This app can be used to plot for many applications and can be used as an online tool

* It can be extended to other types of plots

